Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-16 talk/dls2012/paper.tex
address another reviewer comment

\revd{
It isn't clear from the paper, but a reader might conclude that the bulk of the
time savings are from removing boxing/unboxing operations.
}

@@

We can observe that PyPy (even without loop peeling) is orders of magnitude
faster than CPython. This is due to the JIT compilation
advantages and optimizations we discussed in previous
work~\cite{bolz_allocation_2011, bolz_runtime_2011}. The geometric mean of the
speedup of loop peeling is 70\%, which makes benchmark times
comparable with native-compiled C code. We attribute the performance gap to C code to
the relative immaturity of RPython's JIT machine code backend as well as missing
optimizations, like instruction scheduling. Also, in case of nested loops, 
operations are only moved out of the 
innermost loop. That is an issue when the innermost loop is 
short and a significant amount of time is spent in the outer loops. This is the case 
with for example SparseMatMult.

>>>>

@@

We can observe that PyPy (even without loop peeling) is orders of magnitude
faster than CPython. This is due to the JIT compilation
advantages and optimizations we discussed in previous
work~\cite{bolz_allocation_2011, bolz_runtime_2011}, the main improvement for
these concrete benchmarks come from the allocation removal/unboxing
optimization.

The geometric mean of the
speedup of loop peeling is 70\%, which makes benchmark times
comparable with native-compiled C code. We attribute the performance gap to C code to
the relative immaturity of RPython's JIT machine code backend as well as missing
optimizations, like instruction scheduling. Also, in case of nested loops, 
operations are only moved out of the 
innermost loop. That is an issue when the innermost loop is 
short and a significant amount of time is spent in the outer loops. This is the case 
with for example SparseMatMult.
